---
title: "Lab 9"
author: "Gulalai Shah"
date: "10/26/2020"
output: html_document
---

```{r}
library(stringr)
library(tidyverse)
```
```{r}
library(tidyr)
library(tibble)
```

# 14.3.1 Basic matches
The simplest patterns match exact strings:
```{r}
x <- c("apple", "banana", "pear")
str_view(x, "an")
```
The next step up in complexity is ., which matches any character (except a newline):
```{r}
str_view(x, ".a.")
```
A way to create regular expressions!
```{r}
# To create the regular expression, we need \\
dot <- "\\."
# But the expression itself only contains one:
writeLines(dot)
```

```{r}
x <- c("abc", "a.c", "bef")
str_view(x, "a\\.c")
```
```{r}
x <- "a\\b"
writeLines(x)
```


```{r}
str_view(x, "\\\\")
```

# 14.3.1.1 Exercises
1. Explain why each of these strings don’t match a \: "\", "\\", "\\\".

Each of these strings does not match because they each represent different things. The first string would appear as just a  string, whereas the second string would be represented as “" with the quotation marks included, whereas the third string is represented as”\“, and the fourth string is represented as”\".


# 14.3.2 Anchors

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "^a")
```
```{r}
str_view(x, "a$")
```
```{r}
x <- c("apple pie", "apple", "apple cake")
str_view(x, "apple")
```


```{r}
str_view(x, "^apple$")
```

```{r}
str_view(x, "$^$")
```


# 14.3.2.1 Exercises
1. How would you match the literal string "$^$"?

This should only be matched on the string “^” itself and not include any other strings that might include “^” or be used to detect other strings.



# 14.3.3 Character classes and alternatives
```{r}
# Look for a literal character that normally has special meaning in a regex
x <- c("abc", "a.c", "a*c", "a c")
str_view(x, "a[.]c")
```
```{r}
str_view(x, ".[*]c")
```

```{r}
str_view(x, "a[ ]")
```

```{r}
#To pick either one or the other
x <- c("grey", "gray")
str_view(x, "gr(e|a)y")
```
# 14.3.3.1 Exercises
1. Create regular expressions to find all words that:

•Start with a vowel.
•That only contain consonants. (Hint: thinking about matching “not”-vowels.)
•End with ed, but not with eed.
•End with ing or ise.
```{r}
str_subset(stringr::words, "^[aeiou]")
```

```{r}
# Same things as above but NO MATCHES
str_subset(stringr::words, "[aeiou]", negate=TRUE)
```
```{r}
# Words ending with ed but no eed
str_subset(stringr::words, "[^e]ed$")
```
```{r}
#Words ending with either ing or ise
str_subset(stringr::words, "i(ng|se)$")
```

# 14.3.4 Repetition
```{r}
x <- "1888 is the longest year in Roman numerals: MDCCCLXXXVIII"
str_view(x, "CC?")
```
```{r}
str_view(x, "CC+")
```

```{r}
str_view(x, 'C[LX]+')
```

```{r}
str_view(x, "C{2}")
```

```{r}
str_view(x, "C{2,}")
```
```{r}
str_view(x, "C{2,}")
```

```{r}
str_view(x, 'C{2,3}?')
```

```{r}
str_view(x, 'C[LX]+?')
```


# 14.3.4.1 Exercises
1. Describe the equivalents of ?, +, * in {m,n} form.

? maps to {0,1} which means that there is either 0 or 1 of that character. + maps to {1,} which means that it will match 1 or more than 1 instance of the character. * maps to {0,} which means 0 or more instances



# 14.3.5 Grouping and backreferences
```{r}
str_view(fruit, "(..)\\1", match = TRUE)
```


```{r}
str_view(stringr::words, "(.)\1\1", match = TRUE)
```
# 14.3.5.1 Exercises
Describe, in words, what these expressions will match:
•`(.)\1\1 This would be any character that appears three times in a row.
•"(.)(.)\\2\\1"  This is a pair of characters followed by those same characters but reversed.
•(..)\1:  Two characters that are repeated.
•"(.).\\1.\\1"L  Any character followed by any character followed by the 1st character followed by any character followed by the last character.
•"(.)(.)(.).*\\3\\2\\1" Any three characters followed by zero or more characters of any kind followed by the same three characters but in reverse order.

# 14.4 Tools
Now that you’ve learned the basics of regular expressions, it’s time to learn how to apply them to real problems. In this section you’ll learn a wide array of stringr functions that let you:

•Determine which strings match a pattern.
•Find the positions of matches.
•Extract the content of matches.
•Replace matches with new values.
•Split a string based on a match.

# 14.4.1 Detect matches
```{r}
x <- c("apple", "banana", "pear")
str_detect(x, "e")
```
```{r}
# How many common words start with t?
sum(str_detect(words, "^t"))
```

```{r}
# What proportion of common words end with a vowel?
mean(str_detect(words, "[aeiou]$"))
```

```{r}
# Find all words containing at least one vowel, and negate
no_vowels_1 <- !str_detect(words, "[aeiou]")
```

```{r}
# Find all words consisting only of consonants (non-vowels)
no_vowels_2 <- str_detect(words, "^[^aeiou]+$")
identical(no_vowels_1, no_vowels_2)
```

```{r}
words[str_detect(words, "x$")]
```

```{r}
str_subset(words, "x$")
```

```{r}
df <- tibble(
  word = words, 
  i = seq_along(word)
)
df %>% 
  filter(str_detect(word, "x$"))
```

```{r}
x <- c("apple", "banana", "pear")
str_count(x, "a")

```

```{r}
# On average, how many vowels per word?
mean(str_count(words, "[aeiou]"))
```

```{r}
df %>% 
  mutate(
    vowels = str_count(word, "[aeiou]"),
    consonants = str_count(word, "[^aeiou]")
  )
```

```{r}
str_count("abababa", "aba")
```

```{r}
str_view_all("abababa", "aba")
```
# 14.4.1.1 Exercises
1. For each of the following challenges, try solving it by using both a single regular expression, and a combination of multiple str_detect() calls.

• Find all words that start or end with x.
• Find all words that start with a vowel and end with a consonant.
• Are there any words that contain at least one of each different     vowel?
```{r}
#Either start with x, or end with x
words[str_detect(words, "^x|x$")]
```
```{r}
#All words starting with a vowel, with anything inbetween, and then ending with smething that is not a vowel
str_subset(words, "^[aeiou].*[^aeiou]$")
```

```{r}

#Contain one of each vowel at least
words[str_detect(words, "a") &
  str_detect(words, "e") &
  str_detect(words, "i") &
  str_detect(words, "o") &
  str_detect(words, "u")]
```

# 14.4.2 Extract matches
```{r}
length(sentences)
```
```{r}
head(sentences)
```
```{r}
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
colour_match <- str_c(colours, collapse = "|")
colour_match
```

```{r}
has_colour <- str_subset(sentences, colour_match)
matches <- str_extract(has_colour, colour_match)
head(matches)
```

```{r}
has_colour
```


Can your spot the issue with the regular expression?

FOUND IT! The error is that it takes the word red from reared, so this expression is finding colors where there are none.


```{r}
more <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more, colour_match)
```
```{r}
str_extract(more, colour_match)
```

```{r}
str_extract_all(more, colour_match)
```

```{r}
str_extract_all(more, colour_match, simplify = TRUE)
```

```{r}
x <- c("a", "a b", "a b c")
str_extract_all(x, "[a-z]", simplify = TRUE)
```

# 14.4.2.1 Exercises
1. In the previous example, you might have noticed that the regular expression matched “flickered”, which is not a colour. Modify the regex to fix the problem.


```{r}
# \b indicates a word boundary. THis means only look for actual colors, not peices of words which happen to be colors.
colour_match2 <- str_c("\\b(", str_c(colours, collapse = "|"), ")\\b")
colour_match2
```
```{r}
more2 <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more2, colour_match2, match = TRUE)
```
# 14.4.3 Grouped matches
```{r}
noun <- "(a|the) ([^ ]+)"
has_noun <- sentences %>%
  str_subset(noun) %>%
  head(10)
has_noun %>% 
  str_extract(noun)
```

```{r}
has_noun %>% 
  str_match(noun)
```
```{r}
#library(tidyr)

tibble(sentence = sentences) %>% 
  tidyr::extract(
    sentence, c("article", "noun"), "(a|the) ([^ ]+)", 
    remove = FALSE
  )
```
# 14.4.3.1 Exercises
1. Find all words that come after a “number” like “one”, “two”, “three” etc. Pull out both the number and the word.

```{r}
#Finds a number specified and then any word
number <- "\\b(one|two|three|four|five|six|seven|eight|nine|ten) +(\\w+)"
#Extracts the number and the word
sentences[str_detect(sentences, number)] %>%
  str_extract(number)
```

# 14.4.4 Replacing matches
```{r}
x <- c("apple", "pear", "banana")
str_replace(x, "[aeiou]", "-")
```

```{r}
str_replace_all(x, "[aeiou]", "-")
```

```{r}
x <- c("1 house", "2 cars", "3 people")
str_replace_all(x, c("1" = "one", "2" = "two", "3" = "three"))
```

```{r}
sentences %>% 
  str_replace("([^ ]+) ([^ ]+) ([^ ]+)", "\\1 \\3 \\2") %>% 
  head(5)
```

# 14.4.4.1 Exercises
1. Replace all forward slashes in a string with backslashes.

```{r}
#Tough question, because it knows that \ is an escape character
x <- c("app/le", "p/ear", "bana/na")
str_replace_all(x, "/", "\\\\")
```

# 14.4.5 Splitting

```{r}
sentences %>%
  head(5) %>% 
  str_split(" ")
```
```{r}
"a|b|c|d" %>% 
  str_split("\\|") %>% 
  .[[1]]
```
```{r}
sentences %>%
  head(5) %>% 
  str_split(" ", simplify = TRUE)
```
```{r}
fields <- c("Name: Hadley", "Country: NZ", "Age: 35")
fields %>% str_split(": ", n = 2, simplify = TRUE)
```

```{r}
x <- "This is a sentence.  This is another sentence."
str_view_all(x, boundary("word"))
```
```{r}
str_split(x, " ")[[1]]
```

```{r}
str_split(x, boundary("word"))[[1]]
```
# 14.4.5.1 Exercises
1. Split up a string like “apples, pears, and bananas” into individual components.

```{r}
# The answer in the key does not include the word and, but I am because it makes more sense to me like this based on what the question is asking.
str_split("apples, pears, and bananas", boundary("word"))[[1]]
```



