---
title: "Lab 3A"
author: "Gulalai Shah"
date: "9/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```
```{r, eval=FALSE}
download.file(url="https://ndownloader.figshare.com/files/2292169",
              destfile = "portal_data_joined.csv")
```

```{r}
surveys <- read.csv("portal_data_joined.csv")
```
```{r}
head(surveys)
str(surveys)
```

## Challenge 1
Class: data frame

Rows: 34786

Columns: 13

Species: 48 



## Challenge 2
```{r}
surveys[200, ]
```
```{r}
surveys[nrow(surveys), ]
n_rows <- nrow(surveys) 
```
```{r}
surveys_last <- surveys[n_rows, ]
surveys_last
```
```{r}
surveys_middle <- surveys[n_rows/2, ]
surveys_middle
```
```{r}
surveys_head <- surveys[-(7:n_rows), ]
surveys_head
```
```{r}
sex <- factor(c("male", "female", "female", "male"))
levels(sex)
nlevels(sex)
```
```{r}
sex
```
```{r}
sex <- factor(sex, levels = c("male", "female"))
sex
```
```{r}
year_fct <- factor(c(1990, 1983, 1977, 1998, 1990))
as.numeric(year_fct)
as.numeric(as.character(year_fct))
as.numeric(levels(year_fct))[year_fct]
```

```{r}
plot(as.factor(surveys$sex))
```
```{r}
sex <- factor(surveys$sex)
head(sex)
```
```{r}
levels(sex)
```
```{r}
levels(sex)[1] <- "undetermined"
levels(sex)
```

```{r}
head(sex)
```
## Challenge 3
```{r}
levels(sex)[2:3] <- c("female", "male")
sex <- factor(sex, levels = c("female", "male", "undertermined"))
plot(sex)
```


```{r}
surveys <- read.csv("portal_data_joined.csv", stringsAsFactors = TRUE)
str(surveys)
surveys <- read.csv("portal_data_joined.csv", stringsAsFactors = FALSE)
str(surveys)
surveys$plot_type <- factor(surveys$plot_type)
```

## Challenge 4
```{r}
animal_data <- data.frame(
            animal = c("dog", "cat", "sea cucumber", "sea urchin"), 
            feel = c("furry", "fuzzy", "squishy", "spiny"), 
            weight = c(45, 8, 1.1, 0.8)
            )
```

```{r}
country_climate <- data.frame(
       country = c("Canada", "Panama", "South Africa", "Australia"),
       climate = c("cold", "hot", "temperate", "hot/temperate"),
       temperature = c(10, 30, 18, "15"),
       northern_hemisphere = c(TRUE, TRUE, FALSE, "FALSE"),
       has_kangaroo = c(FALSE, FALSE, FALSE, 1)
       )
str(country_climate)
```
country, climate, temperature, northern_hemisphere are factors
has_kangaroo is numeric

```

```{r}
country_climate <- data.frame(
       country = c("Canada", "Panama", "South Africa", "Australia"),
       climate = c("cold", "hot", "temperate", "hot/temperate"),
       temperature = c(10, 30, 18, 15),
       northern_hemisphere = c(TRUE, TRUE, FALSE, FALSE),
       has_kangaroo = c(FALSE, FALSE, FALSE, TRUE)
       )
str(country_climate)
```

```{r}
str(surveys)
library("lubridate")
```


```{r}
my_date <- ymd("2015-01-01")
str(my_date)
```

```{r}
my_date <- ymd(paste("2015", "1", sep = "-"))
str(my_date)
```

#didn't include the following 2 lines in code because long table

paste(surveys$year, surveys$month, surveys$day, sep = "-")
ymd(paste(surveys$year, surveys$month, surveys$day, sep = "-"))



```{r}
surveys$date <- ymd(paste(surveys$year, surveys$month, surveys$day, sep = "-"))
```

```{r}
str(surveys)
```

```{r}
summary(surveys$date)
```

```{r}
missing_date <- surveys[is.na(surveys$date), c("year", "month", "day")]
head(missing_date)
```





